---
title:  Qualitas Document Formats
author: Peter von Rohr
date: 2016-07-21
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis')
```

```{r DocumentStatus, eval=TRUE}
r6obj_docstat <- rmddochelper::R6ClassDocuStatus$new()
r6obj_docstat$setProject(psProject = "rqudocfmt")
r6obj_docstat$setVersion(psVersion = "0.0.901")
r6obj_docstat$setStatus(psStatus = "Initialisation")
r6obj_docstat$include_doc_stat(psTitle = "## Document Status")
```


```{r TableAbbreviation}
r6ob_abbrtable <- rmddochelper::R6ClassTableAbbrev$new()
### # include table of abbreviations only, if there are any
if (!r6ob_abbrtable$is_empty_abbr())
  r6ob_abbrtable$include_abbr_table(psAbbrTitle = "## Abbreviations")
```

## Disclaimer
This document describes the content of the R-package `rqudocfmt`


## Introduction
`RStudio` together with `rmarkdown`, `knitr` and `pandoc` are great tools to create documents. The property of using templates extensively helps to create documents many different ways. The package `rmarkdown` has built-in functionality to on the one hand use existing templates and on the other hand define new templates that can be used for creating new documents. For more details, please have a look at http://rmarkdown.rstudio.com/developer_document_templates.html and https://blog.rstudio.org/2016/03/21/r-markdown-custom-formats/


## Functionality and format separation
Some specialized formats that are specific for a project or a company should not be placed in a general purpose package which provides functionality for managing documents. Hence those specialized formats are better placed in a separate package which just contains the formats. 


## This package `rqudocfmt`
This package contains all formats that are used at Qualitas AG. Those formats were originally designed as some MS-Office templates. Before being able to use the formats in this package they have to be converted to `rmarkdown`. 


## Example formats
One of the format template is called `project_docu`. This template comes with a company specific title page and with a predefined section structure. A screenshot of the title page of a document based on templated `project_docu` is given below.

```{r project_docu_title_page_graphics}
rmddochelper::insertOdgAsPdf(psOdgFileStem = "project_docu_title_page")
```


## Prerequisites
In order to be able to optimally use the templates in this package `rqudocfmt`, this package must be installed in one of the directories that are accessible via the R-library path. As a result of having `rqudocfmt` installed, `RStudio` also lists the formats when creating a new R Markdown document under `From Template`.





```{r WriteTableOfAbbreviations, results='hide'}
r6ob_abbrtable$writeToTsvFile()
```
<!-- END of document                 -- 
  -- Below this must not be anything --> 
